Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-09 ms.tex
comment

      On the other hand, \citealt{LauerFaber+:2005a} find that $\sim
      60\%$ of cusp galaxies and $\sim29\%$ of core galaxies have
      (generally unresolved) emission in excess of the inward
      extrapolation of the Nuker law, and noted that these nuclei are bluer
      than the background galaxy starlight, suggesting the presence of
      younger stars towards the center of the galaxy.

      In fact it is possible that the mass injection is in fact
      dominated by a nuclear star cluster with a break radius on
      parsec scales. Although this is much smaller than our fiducial
      break radius (100 pc). If the heating is sufficiently high
      moving the break radius inwards would merely change the outer
      gas density profile, without changing the stagnation radius in
      the flow and thus the accretion rate onto the black hole. Of
      course if one moves the break radius to where the stagnation
      radius would be the stagnation radius would move inwards
      somewhat. However note the for high heating rate ($v_w \gsim 500
      $ km/s and small black hole masses $\Mbh \lsim 10^7 \Msun$), we
      predict stagnation radii smaller than a parsec.

>>>>

      On the other hand, \citealt{LauerFaber+:2005a} find that $\sim
      60\%$ of cusp galaxies and $\sim29\%$ of core galaxies have
      (generally unresolved) emission in excess of the inward
      extrapolation of the Nuker law, and noted that these nuclei are bluer
      than the background galaxy starlight, suggesting the presence of
      younger stars towards the center of the galaxy {\bf AG mass
        threshold for this effect}.

      In fact it is possible that the mass injection is dominated by a
      nuclear star cluster with a break radius on parsec
      scales. Although this is much smaller than our fiducial break
      radius (100 pc). If the heating is sufficiently high moving the
      break radius inwards would merely change the outer gas density
      profile, without changing the stagnation radius in the flow and
      thus the accretion rate onto the black hole. Of course if one
      moves the break radius inside where the stagnation radius would
      be for large break radii, the stagnation radius would move
      inwards somewhat. However note the for high heating rate ($v_w
      \gsim 500 $ km/s and small black hole masses $\Mbh \lsim 10^7
      \Msun$), we predict stagnation radii smaller than a parsec.
